Open source landscape ecology tools \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2020-12-16 paper/paper.tex
Add Bivand 2020 Paper

One successful example of an open-source project is the \emph{R} programming language and its extensions (also called packages) \cite{RCoreTeam2019}.
Firstly introduced in 1995 \cite{Smith2016}, today the programming language is among the most popular programming languages, especially in ecology \cite{Lai2019}.
Originally introduced as a statistical programming language, a growing body of packages designed to analyze spatial data subsequently emerged for the \emph{R} programming language \cite{Bivand2006}.
This is documented by the growing \emph{CRAN Task Views: Analysis of Spatial Data} \cite{Bivand2019a} and \emph{Handling and Analyzing Spatio-Temporal Data} \cite{Pebesma2020} that currently list almost 300 packages in total.
Since the task views are maintained manually by just a few people, the actual amount of \emph{R} packages related to spatial data is most likely even higher.
The growing popularity of the \emph{R} programming language for spatial data analysis and landscape ecology can also be seen by the increasing number of related textbooks \cite{Fletcher2019,Lovelace2019,Pebesma2019a}.

@@

To better understand how \emph{R} is used by the landscape ecology community, we conducted a short survey and used mailing lists and social media to reach the community.
In total, the survey was answered by 103 participants, of which the the majority were either ``PhD students'' (34\%), followed by ``Post-Docs'' (28.2\%) and ``Professors'' (12.6\%).
Other, less frequent answers, were ``Data scientists,'' ``None of the above,'' ``Government employees'' ``Master's degree student'' and ``Bachelor's degree student'' (in decreasing order).

@@

We asked the participants to select which terms describe their research topics the best and options that were selected by more than 10\% of participants included ``biodiversity,'' followed by ``land use management,'' ``landscape connectivity'' and ``nature conservation'' (Fig. \ref{fig:fig-survey} A)).

Next, we were interested in the most important tasks to the workflow of the participants.
Not surprisingly, ``(pre-)processing of data,'' ``spatial statistics'' and ``creating maps'' were the most selected options (Fig. \ref{fig:fig-survey} B)).
Interestingly, the available options seemed to describe the most important task to the workflow quite well since only very few participants selected the ``others'' option (all options with less than five total answers were classified as ``others'').

@@

Lastly, when asked how use \emph{R} us currently for landscape ecology, the vast majority of participants answered with either ``very useful'' or ``useful'' (summarized 91.26\%) and only only very few participants evaluated \emph{R} as ``intermediate,'' ``not useful'' or ``not useful at all'' (summarized 8.74\%; Fig. \ref{fig:fig-survey} D)).

@@

MHKH was supported by the German Research Association (DFG) Research Training Group 1644 `Scaling Problems in Statistics,' grant number 152112243.

>>>>

One successful example of an open-source project is the \emph{R} programming language and its extensions (also called packages) \cite{RCoreTeam2019}.
Firstly introduced in 1995 \cite{Smith2016}, today the programming language is among the most popular programming languages, especially in ecology \cite{Lai2019}.
Originally introduced as a statistical programming language, a growing body of packages designed to analyze spatial data subsequently emerged for the \emph{R} programming language \cite{Bivand2006}.
This is documented by the growing \emph{CRAN Task Views: Analysis of Spatial Data} \cite{Bivand2019a} and \emph{Handling and Analyzing Spatio-Temporal Data} \cite{Pebesma2020} that currently list almost 300 packages in total.
Since the task views are maintained manually by just a few people, the actual amount of \emph{R} packages related to spatial data is most likely even higher.
The growing popularity of the \emph{R} programming language for spatial data analysis and landscape ecology can also be seen by the increasing number of related textbooks \cite{Fletcher2019,Lovelace2019,Pebesma2019a}.
A recent overview over the progress of \emph{R} to handle spatial data in general can be found e.g.~here \cite{Bivand2020}.

@@

To better understand how \emph{R} is used by the landscape ecology community, we conducted a short survey and used mailing lists and social media to reach the community.
In total, the survey was answered by 103 participants, of which the the majority were either ``PhD students'' (34\%), followed by ``Post-Docs'' (28.2\%) and ``Professors'' (12.6\%).
Other, less frequent answers, were ``Data scientists'', ``None of the above'', ``Government employees'' ``Master's degree student'' and ``Bachelor's degree student'' (in decreasing order).

@@

We asked the participants to select which terms describe their research topics the best and options that were selected by more than 10\% of participants included ``biodiversity'', followed by ``land use management'', ``landscape connectivity'' and ``nature conservation'' (Fig. \ref{fig:fig-survey} A)).

Next, we were interested in the most important tasks to the workflow of the participants.
Not surprisingly, ``(pre-)processing of data'', ``spatial statistics'' and ``creating maps'' were the most selected options (Fig. \ref{fig:fig-survey} B)).
Interestingly, the available options seemed to describe the most important task to the workflow quite well since only very few participants selected the ``others'' option (all options with less than five total answers were classified as ``others'').

@@

Lastly, when asked how use \emph{R} us currently for landscape ecology, the vast majority of participants answered with either ``very useful'' or ``useful'' (summarized 91.26\%) and only only very few participants evaluated \emph{R} as ``intermediate'', ``not useful'' or ``not useful at all'' (summarized 8.74\%; Fig. \ref{fig:fig-survey} D)).

@@

MHKH was supported by the German Research Association (DFG) Research Training Group 1644 `Scaling Problems in Statistics', grant number 152112243.
